Coupling PDEs on 3D-1D domains with Lagrange multipliers

### 2019-09-25 3d1d_coupled_LM.tex
Adding Paolo's corrections

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively, and we assume that $\min |\D (s)| >0$, where $|\D (s)|$ is the measure of $\D (s)$. 
%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

@@

The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_{\Omega_\ominus} w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

@@

Using a model reduction approach based on averaging, we end up with two different formulations of a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D coupled PDEs.

@@

+\int_\Lambda |\D(s)| \avrd{u_\ominus} \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds

@@

+ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u_\ominus}, \vd)_{\Lambda, |\D|}

@@

\subsubsection*{Problem 1 (3D-1D-3D)}
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
\begin{equation*}
\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
\quad \text{on} \ \partial\mathcal{D}(s)\,,
\end{equation*}
where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
Therefore, the coupling term on $\Gamma$ can be decomposed as,
\begin{equation*}
\int_{\Gamma}\lambda v\, d\sigma
=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
\end{equation*}

Then, we make the following modelling assumptions:
\begin{description}
\item[A3] we assume that the product of fluctuations is small, namely
\begin{equation*}
\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
\end{equation*}
\end{description}
and we obtain 
\begin{equation*}
(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\avrc \lambda, \avrc v)_{\Lambda , |\DD|}  =(f,v)_{\Omega},
\end{equation*}
which, combined with \eqref{eq:1Ddirneu_weak} leads to the second formulation of the reduced problem.

\subsection{Problem 2 (3D-1D-1D)}
Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
\\
&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
\end{align}
\end{subequations}
where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
We notice that all the integrals of the reduced problem are well defined because 
$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following lemma.

@@

\begin{lemma}\label{lemma:H12norm}
Let $\Gamma$ be a tensor product domain, $\Gamma= (0,X) \times (0,Y)$. For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$. Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$. 
Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
\begin{equation*}
\|u\|_{H^{\frac 12}_{00}(\Gamma)}=Y \|u\|_{H^{\frac 12}_{00}(0,X)}.
\end{equation*}
\end{lemma}
\begin{proof}
Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$ and on $(0,X)$ with homogeneous Dirichlet conditions. Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$. In particular,
\begin{align*}
\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( cos\left(\frac{j2\pi y}{Y}\right)+ sin	\left(\frac{j2\pi y}{Y}\right) \right),\\
\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,\\
\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\\
\rho _i = \left(\frac{i\pi}{X}\right) ^2.
\end{align*}
It is easy to verify that 
\begin{eqnarray}
\label{null_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i \\
\label{nonull_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .\\
\end{eqnarray}
Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
\begin{multline*}
\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
\\= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
=  \sum_{i} a_{i,0} \phi_{i}(x).
\end{multline*}
From \cite[Lemma 4.11]{chandler2015interpolation} we have
\begin{equation}\label{H12norm_Gamma}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
\text{ with }
a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
\end{equation}
and 
\begin{equation*}
\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
\text{ with }
\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
\end{equation*}

Therefore, we have
\begin{multline*}
\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=
\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2\\
\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2 =\frac{X^2}{4}\|u\|^2_{H^{\frac 12}(\Gamma)},
\end{multline*}

where we have used the fact that
\begin{eqnarray*}
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}\\
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}.
\end{eqnarray*}
Moreover, in the case in which $u$ is constant with respect to $y$, from \eqref{H12norm_Gamma} we have
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \,dy\,dx \right)^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y)\,  dy dx \right)^2,
\end{multline*}
and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=
\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right) dx\right)^2\\
=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}(0,X)}.
\end{multline*}
\end{proof}

\begin{corollary}
Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$. For any $u\in H^{\frac 12}_{00}(\Gamma)$, let $\avrc{u}(s)= \frac{1}{\sum_i{|X_i|}}\sum_{i=1}^N \int_0^{X_i} u(x,s)\, dx$. Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
\end{corollary}

\begin{corollary}
Let $\Gamma$ be the lateral surface of a cylinder of radius $R$. Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$. Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
\end{corollary}

>>>>

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and let $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that represents the centerline of $\Omega_\ominus$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively, and we assume that $\min |\D (s)| >0$, where $|\D (s)|$ is the measure of $\D (s)$. 
%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

@@

The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.\\

For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_{\Omega_\ominus} w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

@@

Using a model reduction approach based on averaging, we end up with two different formulations of a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D PDEs coupled with Dirichlet-Neumann constraint.

@@

+\int_\Lambda |\D(s)| \avrd{u}_\ominus \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds

@@

+ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u}_\ominus, \vd)_{\Lambda, |\D|}

@@

\subsubsection*{Problem 1 (3D-2D-1D)}
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$ and we exploited the fact that 
\begin{equation*}
\left( \avrc{\lambda}, \vd \right)_{\Lambda, |\DD|} 
= \int _{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \lambda \, d\gamma \right) \vd \, ds 
= (\lambda, \ext \vd)_{\Gamma}.
\end{equation*}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
\begin{equation*}
\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
\quad \text{on} \ \partial\mathcal{D}(s)\,,
\end{equation*}
where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
Therefore, the coupling term on $\Gamma$ can be decomposed as,
\begin{equation*}
\int_{\Gamma}\lambda v\, d\sigma
=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
\end{equation*}

Then, we make the following modelling assumptions:
\begin{description}
\item[A3] we assume that the product of fluctuations is small, namely
\begin{equation*}
\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
\end{equation*}
\end{description}
and the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.  Combined with \eqref{eq:1Ddirneu_weak}, this leads to the second formulation of the reduced problem.

\subsubsection*{Problem 2 (3D-1D-1D)}
Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
\\
&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
\end{align}
\end{subequations}
where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
We notice that all the integrals of the reduced problem are well defined because 
$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following.\\

@@

From the theory of interpolation of Sobolev spaces  illustrated in \cite{chandler2015interpolation}, we can define the fractional norms $\|\cdot \|_{H^{\frac 12}(\Gamma)}$ and $\|\cdot \|_{H^{\frac 12}(\Lambda)}$ as functions of the eigenvalues and eigenfunctions of the Laplacian on $\Gamma$ and $\Lambda$ respectively. In particular, from \cite[Lemma 4.11]{chandler2015interpolation}, if we denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$ with homogeneous Dirichlet condition at the boundary, for any function $u \in H^{\frac 12}_{00}(\Gamma)$ we have
\begin{equation}\label{eq:fracnorm_gamma}
\|u\|_{H^{\frac 12}(\Gamma)}=\left(\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\right)^{\frac 12},
\text{ with }
a_{ij}=\left( u,\phi _{ij} \right)_{\Gamma}.
\end{equation}
Similarly, denoting with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the Laplacian on $\Lambda$ with homogenous Dirichlet boundary conditions, if $u \in H^{\frac 12}(\Lambda)$ we have
\begin{equation}\label{eq:fracnorm_lambda}
\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
\text{ with }
a_i=\left(u, \phi _i \right)_{\Lambda}.
\end{equation}
In the same way, we can define the equivalent weighted norm in $H^{\frac 12}_{00}(\Lambda)$
\begin{equation}\label{eq:weightfracnorm}
\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
\text{ with }
a_i=\left(u, \phi _i \right)_{\Lambda, |\DD|}.
\end{equation}

\begin{lemma}\label{lemma:H12norm}
Let $\Gamma$ be a tensor product domain, $\Gamma= (0,X) \times (0,Y)$. For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$. Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$. 
Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
\begin{equation*}
\|u\|_{H^{\frac 12}_{00}(\Gamma)}=Y \|u\|_{H^{\frac 12}_{00}(0,X)}.
\end{equation*}
\end{lemma}
\begin{proof}
In order to apply \eqref{eq:fracnorm_gamma} and \eqref{eq:fracnorm_lambda}, let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$. Let us also consider the Laplace eigeinproblem on $(0,X)$ with homogeneous Dirichlet conditions. Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$. In particular,
\begin{align*}
\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( cos\left(\frac{j2\pi y}{Y}\right)+ sin	\left(\frac{j2\pi y}{Y}\right) \right),\\
\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,\\
\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\\
\rho _i = \left(\frac{i\pi}{X}\right) ^2.
\end{align*}
It is easy to verify that 
\begin{eqnarray}
\label{null_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i \\
\label{nonull_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .
\end{eqnarray}
Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ form an orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
\begin{multline*}
\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
\\= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
=  \sum_{i} a_{i,0} \phi_{i}(x).
\end{multline*}
%From \cite[Lemma 4.11]{chandler2015interpolation} we have
%\begin{equation}\label{H12norm_Gamma}
%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
%\text{ with }
%a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
%\end{equation}
%and 
%\begin{equation*}
%\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
%\text{ with }
%\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
%\end{equation*}

From \eqref{eq:fracnorm_lambda} we have
\begin{multline*}
\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}
=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2\\
=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2\\
\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2 =\frac{X^2}{4}\|u\|^2_{H^{\frac 12}(\Gamma)},
\end{multline*}
where we have used the fact that
\begin{eqnarray*}
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}\\
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}
\end{eqnarray*}
and we have applied \eqref{eq:fracnorm_gamma} in the last equality.
Moreover, in the case in which $u$ is constant with respect to $y$, we have
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \,dy\,dx \right)^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y)\,  dy dx \right)^2,
\end{multline*}
and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=
\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right) dx\right)^2\\
=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}(0,X)}.
\end{multline*}
\end{proof}
